\chapter{warming up}

\begin{lemma}
  \label{lem:freeIndep_congr}
  \uses{def:FreeIndep}
  Let \((\A,\phi)\) be a probability space, and let \((\A_i)_{i\in I}\) and \((\B_i)_{i\in I}\) be
  families of subalgebras with \(\A_i = \B_i\) for all \(i\). Then if \((\A_i)_{i \in I}\) is freely
  independent, so is \((\B_i)_{i\in I}\).
\end{lemma}
\begin{proof}
  by extentionality of families.
\end{proof}

\begin{lemma}
  \label{lem:freeIndep_of_inj}
  \uses{lem:freeIndep_congr}
  Let \((\A,\phi)\) be a probability space, and let \((\A_i)_{i\in I}\) be a family of
  freely independent subalgebras. Additionally, let \(f:J \rightarrow I\) be an injective map. Then the family
  \((\A_{f(j)})_{j\in J}\) is freely independent.
\end{lemma}
\begin{proof}
  This follows quite readily. Let \((a_k)_{k\in [n]}\) be a finite sequence of centered elements
  with alternating \(J\)-labeling \(g:[n]\rightarrow J\), such that \(a_k \in \A_{f(g(k))}\).
  Then \(f \o g\) is an alternating \(I\)-labeling for that sequence: given adjacent \(k,k' \in [n]\),
  since \(g(k)\) and \(g(k')\) are distinct, and \(f\) is injective, so are \(f(g(k))\) and \(f(g(k'))\).
  Then, since \((\A_i)_{i\in I}\) is freely independent, we have that the product of \((a_k)_{k\in [n]}\)
  is balanced, concluding the proof. As a note for formalizing, it may be useful to prove this
  for any \((\mathcal{B}_j){j\in J}\) with \(\mathcal{B}_j = \A_{f(j)}\), allowing you to abstract these families.
\end{proof}

\begin{lemma}

\end{lemma}

\begin{lemma}
  \label{lem:mem_iSup_induction_balanced}
  Let \((\A,\phi)\) be a probability space, let \((\A_i)_{i\in I}\) be a family of subalgebras,
  let \(f:J \rightarrow I\) be a map, and let \(a \in \bigcup_{f(i)=j} \A_i\) for some \(j\).
  Then (something something a is a sum of products of balanced elements, plus a constant term)
\end{lemma}



\begin{lemma}
  \label{lem:freeIndep_iUnion}
  Let \((\A,\phi)\) be a probability space, and let \((\A_i)_{i\in I}\) be a family of
  freely independent subalgebras. Additionally, let \(f:I \rightarrow J\) be any map.
  Define \(\B_j := \text{alg}\left(\bigcup_{f(i)=j} \A_i\right)\) for all \(j\in J\).
  Then \((B_j)_{j\in J}\) is freely independent. note: Maybe use isup notation?
\end{lemma}
\begin{proof}
  let \((a_k)_{k\in[n]}\) be a finite sequence of balanced elements, and let \(g:[n]\rightarrow J\)
  be an alternating \(J\)-labeling such that \(a_k \in \B_{g(k)}\) for all \(k \in [n]\).


\end{proof}
